---
title: "Fitbit & ET Glasses - Methods"
output: html_notebook
---
```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Packages
# install.packages("needs")
# Choose "No"
library(needs)
needs(tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS)
```


# Initial Preparations

Run following Code if and only if new data is added to the initial data.

```{r message=FALSE, warning=FALSE,include=FALSE}
source(file = "data.wrangling.R")
```
# ET Glasses

## Acceleration

The Tobii Glases record acceleration data with a frequency of 100Hz. Therefore it should be possible to calculate the walked distance wearing the glasses using the following formulas:

$$\Delta x_{d,i} = 0.5 (t_{i-1}-t_{i})^2, \text{ with }i=2,...,t_n; d = z,x$$

$$x_d=\sum_{i=1}^n |\Delta x_{d,i}|, \text{ with }i=2,...,t_n; d = z,x$$

$$\sum x=\sqrt{x_z^2+x_x^2}$$

Using these formulas, one brave assumption must be made, that is, for every time period the initial velocity is equal to 0.

The real data gives plausible values.

```{r}
df_meter_real <- read_rds(file = "final_data/meter_real.rds")
df_meter_real
summary(df_meter_real$ges)
```

On the contrary, simulated situations revealed multiple problems. 

For the first simulation the participant was standing still without moving its head and with stong movements of the head respectively. A reliable measurement would give the same distance for both situations. 
Afterwards, we simulated two two times 5 meter long walks. One time the participant turned around after 5 meters. During the other walk the participant walked 5 meters and walked back backwards. Again, we expect the glasses to give the same walking distance.
To test real world situations we simulated two random walks in a simulated class room. One walk simulated an extensive walk and the other walk simulated a less intense walk.
Additionally, we tested the values for taking the elevator and walking a staircase.
The simulated situations give the following values.

```{r}
df_meter_sim <- read_rds(file = "final_data/meter_test.rds")

df_meter_sim
```
Plotting the acceleration reveals the problems with the acceleration data.

```{r}
df_meter_sim_time <- read_rds(file = "final_data/meter_test_time.rds")

df_meter_sim_time %>%
  pivot_longer(cols = contains("acc"),
               names_to = "acc") %>%
ggplot(mapping = aes(x = time,
                     y = value
                     )
       ) +
  geom_path() +
  labs(y = "") +
  theme(text = element_text(family = "serif")) +
  facet_grid(rows = vars(name),
             cols = vars(acc) 
             ) +
  theme(strip.text.y = element_text(angle = 0))
```

## Pupil Dialation

The ET Glasses report the pupil dilation at a frequency of 100 Hz. 

```{r}
# df_dil <- read_rds(file = "final_data/dilation.rds")
# 
# df_dil %>%
#   pivot_longer(cols = right:left,
#                names_to = "dilation") %>%
# ggplot(mapping = aes(x = time,
#                      y = value
#                      )
#        ) +
#   geom_path() +
#   facet_grid(rows = vars(ID),
#              cols = vars(dilation)
#              )
```

# FitBit

All participants were given a FitBit Smart Watch to wear during the experiment. 

## Heart Rate

The heart rate of each participant were measured during the experiment.

```{r}
# Plots

df_heart_all <-
  read_rds(file = "final_data/heart_all.rds") |> 
  mutate(status = factor(status,
                         levels = c("Expert","Novice"),
                         labels = c("Expert","Novice")
                         )
         )

df_heart_min <-
  read_rds(file = "final_data/heart_min.rds")

df_heart_aggr <- 
  read_rds(file = "final_data/heart_aggr.rds") |> 
  mutate(status = factor(status,
                         levels = c("Novice","Expert"),
                         labels = c("Novice","Expert")
                         )
         )

plot_flow <-
ggplot(data = df_heart_all,
       mapping = aes(x = as.numeric(Time),
                     y = `Heart Rate`,
                     group = ID)
       ) +
  geom_line(mapping = aes(color = status),
            size = 0.3,
            alpha = 1
            ) +
  xlim(0, min(df_heart_min$min)) +
  scale_color_viridis_d(option = "A",
                       end = 0.8)  +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Time (in Seconds)",
       y = "Heart Rate\n(in Beats per Minute)") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.position = "none",
        strip.text = element_text(size = 16)) +
  facet_grid(cols = vars(Type),
             scales = "free_x")

plot_flow_leg <-
ggplot(data = df_heart_all,
       mapping = aes(x = Time,
                     y = `Heart Rate`
                     )
       ) +
  geom_smooth(mapping = aes(color = status),
              method = "loess") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
 # scale_linetype_manual(values = c(1, 6)) +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.title = element_blank()) 

legend <- cowplot::get_legend(plot_flow_leg)

plot_loess <-
ggplot(data = filter(df_heart_all),
       mapping = aes(x = as.numeric(Time),
                     y = `Heart Rate`
                     )
       ) +
  stat_smooth(geom = "line",
              mapping = aes(color = status),
              method = "loess",
              se = FALSE) +
  xlim(0,min(df_heart_min$min)) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Time (in Seconds)",
       y = "Heart Rate\n(in Beats per Minute)") +
  theme_minimal() +
  facet_grid(cols = vars(Type),
             scales = "free_x",
             ) +
  theme(text = element_text(family = "serif"),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()
        )

plot_box <- 
ggplot(data = df_heart_aggr,
       mapping = aes(x = Type,
                     y = mean,
                     color = status
                     )
       ) +
  geom_boxplot(color = "darkgrey",
               fill = "grey") +
  geom_line(data = filter(df_heart_aggr,
                          status == "Novice"),
            mapping = aes(x = Type,
                          y = mean,
                          group = as_factor(ID)
                          ),
            linetype = 1,
            alpha = 0.5
            ) +
  geom_line(data = filter(df_heart_aggr,
                          status == "Expert"),
            mapping = aes(x = Type,
                          y = mean,
                          group = as_factor(ID)
                          ),
            linetype = 6,
            alpha = 0.5
            ) +
  geom_point(size = 2,
             alpha = 0.5) +
  labs(x = "",
       y = "Average Heart Rate\n(in Beats per Minute)") +
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        strip.text = element_blank(),
       legend.position = "none",
        axis.text.x = element_blank()
        ) +
  aes(fill = Type)

lo_mat <- rbind(c(1,1,1,1,1,1,NA),
                c(2,2,2,2,2,2,4),
                c(3,3,3,3,3,3,NA))

plot_heart <- 
grid.arrange(grobs = list(plot_flow, plot_loess, plot_box, legend),
             layout_matrix = lo_mat)

plot_heart
```

## Steps

Using the FitBit we could also measure the steps a person walked. Unfortunately, the measurement was not as reliable as hoped. To confirm, we should simulate situations with a fixed number of steps.

```{r}
df_steps <- read_rds(file = "final_data/steps.rds")
set.seed(5678)
ggplot(data = df_steps,
       mapping = aes(x = type,
                     y = Steps
                     )
       ) +
  geom_boxplot(mapping = aes(color = type),
               fill = "grey",
               alpha = 0.6) +
  geom_jitter(mapping = aes(color = type),
              alpha = 0.9,
              width = 0.3) + 
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  labs(x = "",
       y = "Steps During\nMain Phase") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()
        ) 
```

# Combined Analysis

## Steps and Heart Rate

```{r}
ggplot(data = df_steps,
       mapping = aes(x = Steps,
                     y = mean)
       ) +
  geom_point(mapping = aes(shape = type,
                           color = type),
             alpha = 0.7,
             size = 2.5) +
    geom_smooth(mapping = aes(color = type),
              method = "lm",
              se = F) +
  scale_color_viridis_d(option = "A",
                       end = 0.8
                       ) +
  labs(x = "Steps",
       y = "Average Heart Rate\n(in Beats per Minute)"
       ) +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        legend.title = element_blank(),
        )
```

## Heart Rate and Pupil Dilation

```{r}
df_dil_aggr <- read_rds(file = "final_data/heart_dilation.rds")

df_dil_aggr %>%
  pivot_longer(cols = contains("dil"),
               names_to = "left_right",
               values_to = "Dilation") %>%
  mutate(type = factor(type,
                       levels = c("Expert","Novice"),
                       labels = c("Expert","Novice")
                       )
         ) |> 
  ggplot(mapping = aes(x = heart_rate_z,
                       y = Dilation)) +
  geom_point(mapping = aes(color = type),
             alpha = 0.7) +
  scale_color_viridis_d(option = "A",
                       end = 0.8) +
  geom_smooth(method = "lm",
              linetype = 2,
              color = "darkviolet") +
  labs(x = "Heart Rate\n(z-standardized)") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        text = element_text(family = "serif")) +
  facet_grid(cols = vars(factor(left_right,
                                levels = c("dil_left_z","dil_right_z"),
                                labels = c("Left Eye","Right Eye")
                                )
                         )
             ) 
```

# Measuring 

```{r, warning=FALSE, message=FALSE}
df_heart_all %>% 
  clean_names() %>% 
  pivot_wider(names_from = time,
              values_from = heart_rate,
              names_prefix = "x")  %>%
  select(!contains("x")) ->
data_cache 

df_heart_all %>% 
  clean_names() %>% 
  pivot_wider(names_from = time,
              values_from = heart_rate,
              names_prefix = "x")  %>%
  filter(id == "101") %>% 
  rowwise() %>%
  na_mean() %>%
  pivot_longer(cols = contains("x"),
               names_to = "time",
               values_to = "heart_rate") %>% 
  mutate(time = str_remove_all(time, "x")) %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_line()
  
  
 mutate(id = data_cache$id,
        ) %>% 
 right_join(x = ., 
            y = data_cache,
            by = "id") %>% 
 pivot_longer(cols = contains("x"),
               names_to = "time",
               values_to = "heart_rate") %>%
  mutate(time = str_remove_all(string = time,
                               pattern = "x"),
         time = as.numeric(time),
         heart_rate = as.numeric(heart_rate),
         id = as_factor(id)) %>%
  filter(id == "101") %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate,
                       group = id)
       ) + 
  geom_line(mapping = aes(color = status),
            size = 0.3,
            alpha = 1
            ) +
  xlim(0, min(df_heart_min$min)) +
  facet_grid(cols = vars(type))

  df_heart_all_wide

for (i in colnames(df_heart_all_wide)[-1:-4]) {
  
  df_heart_all_wide %>% 
    select(i)
  
}
df_heart_all_wide %>% 
  select(contains("x")) %>%
  as.matrix() %>% 
  rowwise() %>% 
  na_kalman() %>% 
  as_tibble() ->
  imp

imp$id <- data_cache$id

left_join(data_cache, imp,
          by = "id") %>% 
   pivot_longer(cols = contains("x"),
               names_to = "time",
               values_to = "heart_rate") %>%
  filter(id == "101") %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate,
                       group = id)
       ) + 
  geom_line(mapping = aes(color = status),
            size = 0.3,
            alpha = 1
            )

df_heart_all %>% 
  clean_names() %>% 
  pivot_wider(names_from = time,
              values_from = heart_rate,
              names_prefix = "x")  %>%
  filter(id == "101", type == "Post") %>% 
  select(!c("id","type","status")) %>% 
  pivot_longer()
  na_kalman()


imp <- na_kalman(tsAirgap)
ggplot_na_imputations(tsAirgap, imp)



df_heart_all %>% 
  clean_names() %>% 
  pivot_wider(names_from = time,
              values_from = heart_rate,
              names_prefix = "x") %>% 
  pivot_longer(cols = contains("x"),
               names_to = "time",
               values_to = "heart_rate") %>% 
  group_by(id, type) %>% 
  mutate(heart_rate = na_kalman(heart_rate)) %>% 
  ungroup() %>% 
  ggplot(mapping = aes(x = time, 
                       y = heart_rate,
                       group = id
                       )
         ) +
  geom_line()


```



