---
title: "Through the eyes of the teacher - Multimodal exploration of expertise differences
  in the perception of classroom disruptions in a laboratory study"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r include=FALSE}
# install.packages("needs")

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych)

```

## Participants
```{r demographicstable, include = TRUE, echo=FALSE}

# read in data and select and rename relevant columns with transmute 
demo.data <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  filter(!LI06_05 == 201) %>% # exclude participant due to missing eye tracking data
  transmute(Group = LI06_05,
            Gender = LI02_01_1,
            Age = LI03_01,
            `Teaching Experience` = LI04_01,
            School_type = LI18,
            Grade = LI16_05,
            Subject = LI10_05,
            Semester = LI11_01,
            Internship = LI13_01,
            `Extracurricular Teaching Experience` = LI14,
            `Secondary Teaching Activities` = LI17
            )

# define expert and novice with ifelse function
demo.data$Group = ifelse(demo.data$Group < 200, "Novice","Expert")

# changing gender to count female gender (male = 2 --> 0)
demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")

# changing character Gender into numeric
demo.data$Gender <- as.numeric(demo.data$Gender)

# creating new column with total participants to calculate percent of gender
demo.data <- demo.data %>%
  group_by(Group) %>%
  mutate(Sum_participants = n())

# replacing 2 to 1 (Oberschule = Gymnasisium --> Secondary school)
demo.data$School_type[demo.data$School_type == 2] <- "1"

# creating new column to calculate percent of school type
demo.data <- 
  demo.data %>%
  group_by(School_type, Group) %>%
  mutate(Count_Schooltype = sum(n())) %>% 
  mutate(Percent_schooltype = round((Count_Schooltype/Sum_participants) * 100, 
         digits = 2))

# changing character Percent_schooltype into numeric
demo.data$Percent_schooltype <- as.numeric(demo.data$Percent_schooltype)

# changing character Semester into numeric
demo.data$Semester <- as.numeric(demo.data$Semester)


# changing Type of School into character
# LI18:
# 1: Grundschule
# 2: Oberschule
# 3: Gymnasium
# 4: Förderschule/Sondershausen
# 5: Berufsbildende Schule
# -1: andere Schulform
demo.data$School_type <- factor(x = demo.data$School_type,
                   levels = c("1","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$School_type)
                   labels = c("Primary School","Secondary School", "Special Education","Vocational School", "Other Schooltype")) # Bezeichnungen

# changing `Extracurricular Teaching Experience` to count experience (no experience = 2 --> 0)
demo.data$`Extracurricular Teaching Experience` = ifelse(demo.data$`Extracurricular Teaching Experience` == 1, "1","0")

# changing character Extra. Exp. into numeric
demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)

# changing `Secondary Teaching Activities` to count experience (no experience = 2 --> 0)
demo.data$`Secondary Teaching Activities` = ifelse(demo.data$`Secondary Teaching Activities` == 1, "1","0")

# changing character Extra. Exp. into numeric
demo.data$`Secondary Teaching Activities` <- as.numeric(demo.data$`Secondary Teaching Activities`)

# create new columns that give proportion of Gender
# percent = female gender divided by all female Gender
# demo.data <- demo.data  %>% 
#   group_by(Group) %>% 
#   mutate(Gender_percent = Gender/Sum_participants) %>% 
#   mutate(Gender_percent = round(sum(Gender_percent)*100, digits=0))

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Women in percent" = round(sum(Gender/Sum_participants) * 100, 
                                               digits = 2),
            "M Age in years" = round(mean(Age), 
                                     digits = 2),
            "SD Age in years" = round(sd(Age), 
                                      digits = 2),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
                       "M Exp." = round(mean(`Teaching Experience`), 2),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`)
            )

knitr::kable(demo.table,
             caption = "Demographic information & teaching experience")


# # create a basic table (tibble) using tidyverse functions
# exp.table <- demo.data %>%
#   group_by(Group) %>%
#   summarise(N=n(),
#            "M Exp." = round(mean(`Teaching Experience`), 2),
#             "SD Exp." = round(sd(`Teaching Experience`), 2),
#             "Min Exp." = min(`Teaching Experience`),
#             "Max Exp." = max(`Teaching Experience`),
#             "M Semester" = round(mean(Semester), 2),
#             "SD Semester" = round(sd(Semester), 2),
#             "Min Semester" = min(Semester),
#             "Max Semester" = max(Semester),
#             "M Internship" = round(mean(Internship), 2),
#             "SD Internship" = round(sd(Internship), 2),
#             "Min Internship" = min(Internship),
#             "Max Internship" = max(Internship),
#             "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Sum_participants) * 100, digits = 2),
#             "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Sum_participants) * 100)
#            )

```

## Measures

### Eye-Tracking Data
```{r eyetracking, include = TRUE, echo=FALSE}

# return a character vector with names of .tsv data in data folder
 file_names <- list.files(path = "data",
                          pattern = "interval_complete.tsv")

# read every object names in file_names and save it as a tibble
 for (i in file_names) {

   work_data <-
     read_tsv(file = paste0("data/", i),
              locale = locale(decimal_mark = ",")) %>%
     dplyr::select(Group,
                   Participant,
                   starts_with("Total_duration_of_fixations"),
                   starts_with("Number_of_fixations")
     )

   assign(value = work_data, 
          x = str_remove(paste0("tib_", i), 
                         pattern = ".tsv")) 

 }

# Bind every tibble that contains "interval_complete" to a new tible
 df_aoi <-
   mget(ls(pattern = "interval_complete")) %>%
   bind_rows()
   
 
 df_aoi$Participant <- as.numeric(
   str_extract(df_aoi$Participant,
                                   "\\d{3}")
   )

# Remove temporary data for a cleaner workspace
 rm(list = ls(pattern = "^tib_ProVisio"))
 rm(work_data)
 rm(file_names)
 rm(i)

```


#### Fixation count & fixation duration (M, SD, Effektstärke)
•	Alles (gesamte Lektion), students (gesamte Lektion)
•	disruptive person (tatsächliche Dauer der Störung)

#### Time to first fixation 
•	disruptive person (tatsächliche Dauer der Störung)


### Rating Scales (Disruption Appraisal, Confidence Appraisal, Prevalence Rating)
```{r rating_scales, echo=FALSE, results='asis'}

# read in data and combine multiple excel sheets into a single table 
sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    ) %>%
  mutate(ID = ifelse(ID < 200, "Novice", "Expert"))

############## Disruption appraisal #########################

sri.disrup.table <-
  sri %>%
  group_by(ID) %>%
  summarise(
    N = n(),
    "M" = round(mean(disruption_appraisal), digits = 2),
    "SD" = round(sd(disruption_appraisal), digits = 2),
    "Min" = min(disruption_appraisal),
    "Max" = max(disruption_appraisal)
    )

knitr::kable(sri.disrup.table,
             caption = "Disruption Appraisal")

### with event
sri.disrup.event.table <-
  sri %>%
  group_by(ID, event) %>%
  summarise(
    N = n(),
    "M" = round(mean(disruption_appraisal), digits = 2),
    "SD" = round(sd(disruption_appraisal), digits = 2),
    "Min" = min(disruption_appraisal),
    "Max" = max(disruption_appraisal)
  )

# insert a table into HTML
knitr::kable(sri.disrup.event.table,
             caption = "Disruption appraisal with event")

# create a new data frame with appraisal
sri_disrup <- subset.data.frame(sri, select = c(ID, event, disruption_appraisal))

# plotting disruption appraisal for groups
dist_group_plot <- 
  sri_disrup %>% 
  mutate(ID = factor(ID,
                     levels = c("Novice",
                                "Expert"
                                )
                     )
         ) %>% 
  ggplot(mapping = aes(x = ID,
                       y = disruption_appraisal)) +
  geom_boxplot(mapping = aes(fill = ID),
               outlier.shape = NA) +
  geom_point(size = 1,
             alpha = 0.4,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  scale_x_discrete(limits = c("Novice", "Expert")) +
  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
  labs(x = "",
       y = "Disruption Appraisal") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("How disruptive was the event for you?") +
  theme_cowplot()

dist_group_plot


#################### T-TEST & EFFECT SIZE ############

# Disruption appraisal 
# t-test for expertise differences
t_test_disrup <- t.test(x = sri$disruption_appraisal[sri$ID == "Expert"],
                        y = sri$disruption_appraisal[sri$ID == "Novice"])

# Disruption appraisal 
# effect size for expertise differences
d_sri_disrup <- CohenD(x = sri$disruption_appraisal[sri$ID == "Expert"],
                       y = sri$disruption_appraisal[sri$ID == "Novice"],
                       na.rm = TRUE)

round(d_sri_disrup, 2)



############## Confidence appraisal #########################

sri.confi.table <-
  sri %>%
  group_by(ID) %>%
  summarise(
    "M" = round(mean(confidence_appraisal), digits = 2),
    "SD" = round(sd(confidence_appraisal), digits = 2),
    "Min" = min(confidence_appraisal),
    "Max" = max(confidence_appraisal)
  )

# insert a table into HTML
knitr::kable(sri.confi.table,
             caption = "Confidence appraisal")

### with event
sri.confi.event.table <- 
  sri %>%
  group_by(ID, event) %>%
  summarise(
    N = n(),
    "M" = round(mean(confidence_appraisal), digits = 2),
    "SD" = round(sd(confidence_appraisal), digits = 2),
    "Min" = min(confidence_appraisal),
    "Max" = max(confidence_appraisal)
  )

knitr::kable(sri.confi.event.table,
             caption = "Confidence appraisal with event")

# create a new data frame with appraisal
sri_confi <- subset.data.frame(sri, 
                               select = c(ID, 
                                          event, 
                                          confidence_appraisal)
                               )

# plotting confidence appraisal for groups
confi_group_plot <- 
  sri_confi %>% 
  mutate(ID = factor(ID,
                     levels = c("Novice",
                                "Expert"
                                )
                     )
         ) %>% 
  ggplot(mapping = aes(x = ID,
                       y = confidence_appraisal)) +
  geom_boxplot(mapping = aes(fill = ID),
               outlier.shape = NA) +
  geom_point(size = 1,
             alpha = 0.4,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  scale_x_discrete(limits = c("Novice", "Expert")) +
  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
  labs(x = "",
       y = "Confidence Appraisal") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("How confident did you feel dealing with this event?") +
  theme_cowplot()

confi_group_plot

#################### T-TEST & EFFECT SIZE ############

# Confidence Appraisal 
# t-test for expertise differences
t_test_confi <- t.test(x = sri$confidence_appraisal[sri$ID == "Expert"],
                       y = sri$confidence_appraisal[sri$ID == "Novice"])

# Disruption Factor 
# effect size for expertise differences
d_sri_confi <- CohenD(x = sri$confidence_appraisal[sri$ID == "Expert"],
                      y = sri$confidence_appraisal[sri$ID == "Novice"],
                      na.rm = TRUE)

round(d_sri_confi, 2)


############## Prevalence Rating #########################

sri.preva.table <-
  sri %>%
  group_by(ID) %>%
  summarise(
    N = n(),
    "M" = round(mean(prevalence_rating), digits = 2),
    "SD" = round(sd(prevalence_rating), digits = 2),
    "Min" = min(prevalence_rating),
    "Max" = max(prevalence_rating)
  )

# insert a table into HTML
knitr::kable(sri.preva.table,
             caption = "Prevalence rating")

#### with event 
sri.preva.event.table <-
  sri %>%
  group_by(ID, event) %>%
  summarise(
    N = n(),
    "M" = round(mean(prevalence_rating), digits = 2),
    "SD" = round(sd(prevalence_rating), digits = 2),
    "Min" = min(prevalence_rating),
    "Max" = max(prevalence_rating)
  )

# insert a table into HTML
knitr::kable(sri.preva.event.table,
             caption = "Prevalence rating with events")

# create a new data frame with rating
sri_preva <- subset.data.frame(sri, select = c(ID, event, prevalence_rating))

# plotting prevalence rating for groups
preva_group_plot <- 
  sri_preva %>% 
  mutate(ID = factor(ID,
                     levels = c("Novice",
                                "Expert"
                                )
                     )
         ) %>% 
  ggplot(mapping = aes(x = ID,
                       y = prevalence_rating)) +
  geom_boxplot(mapping = aes(fill = ID),
               outlier.shape = NA) +
  geom_point(size = 1,
             alpha = 0.4,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  scale_x_discrete(limits = c("Novice", "Expert")) +
  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
  labs(x = "",
       y = "Prevalence Rating") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("How widespread is this event in the classroom?") +
  theme_cowplot()

preva_group_plot


#################### T-TEST & EFFECT SIZE ############

# Prevalence Rating 
# t-test for expertise differences
t_test_preva <- t.test(x = sri$prevalence_rating[sri$ID == "Expert"],
                       y = sri$prevalence_rating[sri$ID == "Novice"])

# Prevalence Rating 
# effect size for expertise differences
d_sri_preva <- CohenD(x = sri$prevalence_rating[sri$ID == "Expert"],
                      y = sri$prevalence_rating[sri$ID == "Novice"],
                      na.rm = TRUE)

round(d_sri_preva, 2)

```

### Situational Jugdement Test
```{r sjt, echo=FALSE, results='asis'}

# read in data
df_sjt <- 
  read_excel("./data/SJT.xlsx") 

# select relevant columns --> only subject ID and mean 
df_sjt <- df_sjt %>%
  dplyr::select(UI06_05, # ID
         SJT_AL_gek, # Monitoring
         SJT_ST_gek, # Managing momentum
         SJT_R_gek, # Rules and routines
         SJT_KF_gek) %>% # All
  filter(!UI06_05 == 201) # exclude ID with no eye tracking data

# remove NAs
df_sjt <- na.omit(df_sjt)


# rename columns
df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
                           "Monitoring" = "SJT_AL_gek",
                           "Managing momentum" = "SJT_ST_gek",
                           "Rules and routines" = "SJT_R_gek",
                           "All" = "SJT_KF_gek"))


# changing from wide to long format
df_sjt_long <- df_sjt %>% 
  pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")

# define expert and novice with ifelse function
df_sjt_long$Group = ifelse(df_sjt_long$Group < 200, "Novice","Expert")


#################### N, MEAN & SD ############

# mean & SD SJT ALL
sjt_mean <- df_sjt_long %>%
  filter(`Facets Classroom Management` == "All") %>%
  group_by(Group) %>%
  summarise(N = n(),
            "M" = round(mean(Mean), 2),
            "SD" = round(sd(Mean), 2), 
            "Min" = round(min(Mean), 2),
            "Max" = round(max(Mean), 2), 
            )

# insert a table into HTML
knitr::kable(sjt_mean,
             caption = "N, M and SD for overall value")


# mean SJT Managing Momentum
sjt_mm <- df_sjt_long %>%
  filter(`Facets Classroom Management` == "Managing momentum") %>%
  group_by(Group) %>%
  summarise(N = n(),
            "M" = round(mean(Mean), 2),
            "SD" = round(sd(Mean), 2), 
            "Min" = round(min(Mean), 2),
            "Max" = round(max(Mean), 2), 
            )

# insert a table into HTML
knitr::kable(sjt_mm,
             caption = "N, M and SD for managing momentum")


# mean SJT Monitoring
sjt_m <- df_sjt_long %>%
  filter(`Facets Classroom Management` == "Monitoring") %>%
  group_by(Group) %>%
  summarise(N = n(),
            "M" = round(mean(Mean), 2),
            "SD" = round(sd(Mean), 2), 
            "Min" = round(min(Mean), 2),
            "Max" = round(max(Mean), 2), 
            )

# insert a table into HTML
knitr::kable(sjt_mean,
             caption = "N, M and SD for monitoring")


# mean SJT Rules and routins
sjt_r <- df_sjt_long %>%
  filter(`Facets Classroom Management` == "Rules and routines") %>%
  group_by(Group) %>%
  summarise(N = n(),
            "M" = round(mean(Mean), 2),
            "SD" = round(sd(Mean), 2), 
            "Min" = round(min(Mean), 2),
            "Max" = round(max(Mean), 2), 
            )

# insert a table into HTML
knitr::kable(sjt_mean,
             caption = "N, M and SD for rules and routines")


#################### Plots ############

# plotting mean of all aspects 
mean_plot <- 
df_sjt_long %>% 
  mutate(Group = factor(Group,
                        levels = c("Novice", 
                                   "Expert")
                        )
         ) %>% 
  ggplot(mapping = aes(x = Group,
                       y = Mean)) +
  geom_boxplot(mapping = aes(fill = Group), 
               outlier.shape = NA) +
  geom_point(size = 1, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1,
                                        height = 0.1)) +
  labs(x = "") +
  ylim(0,1) + 
  scale_fill_brewer(palette  = "RdBu") +  
  facet_wrap(vars(`Facets Classroom Management`), 
             nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("SJT") +
    theme(
    plot.title = element_text(size = 25, 
                              face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 22)
        )

mean_plot


#################### T-TEST & EFFECT SIZE ##################

# define expert and novice with ifelse function in wide format
df_sjt$Group = ifelse(df_sjt$Group < 200, "Novice","Expert")

#### ALL #### 
# t-test for expertise differences 
t.test(x = df_sjt$All[df_sjt$Group == "Expert"],
       y = df_sjt$All[df_sjt$Group == "Novice"])


# effect size for expertise differences
d_sjt_all <- CohenD(x = df_sjt$All[df_sjt$Group == "Expert"],
                    y = df_sjt$All[df_sjt$Group == "Novice"],
                    na.rm = TRUE
                    )

round(d_sjt_all, 2)

#### MANAGING MOMENTUM #### 
# t-test for expertise differences 
t.test(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
       y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"]
       )


# effect size for expertise differences
d_sjt_mm <- CohenD(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
                   y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
                   na.rm = TRUE
                  )

round(d_sjt_mm, 2)

#### MONITORING ####
# t-test for expertise differences 
t.test(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
       y = df_sjt$Monitoring[df_sjt$Group == "Novice"]
       )


# effect size for expertise differences
d_sjt_moni <- CohenD(x = df_sjt$Monitoring[df_sjt$Group == "Expert"],
                     y = df_sjt$Monitoring[df_sjt$Group == "Novice"],
                     na.rm = TRUE
                    )

round(d_sjt_moni, 2)


#### RULES & ROUTINES #### 
# t-test for expertise differences 
t.test(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
       y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"]
      )


# effect size for expertise differences
d_sjt_rr <- CohenD(x = df_sjt$`Rules and routines`[df_sjt$Group == "Expert"],
                   y = df_sjt$`Rules and routines`[df_sjt$Group == "Novice"],
                   na.rm = TRUE
                  )

round(d_sjt_rr, 2)

```


### Classroom Questionnaire
```{r classroom questionnaire, echo=FALSE, results='asis'}

# load data files with modified scales
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LI06_05,
                LM01_01:LM01_08, # classroom management 
                LP01_01:LP01_08) %>% # non- & paraverbal communication 
  filter(!LI06_05 == 201) %>% # exclude ID with no eye tracking data
  mutate(LI06_05 = ifelse(LI06_05 < 200, "Novice", "Expert")) %>% 
  rename(Group = LI06_05)

# remove NAs
df_quest <- na.omit(df_quest)

# create table with means
df_quest_table <-
  df_quest %>%
  group_by(Group) %>%
  transmute(
    Group = Group,
    # "N cm" = length(c_across(starts_with("LM")), na.rm = TRUE),
    "M cm" = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
    "SD cm" = round(sd(c_across(starts_with("LM")), na.rm = TRUE), 2),
    "Min cm" = round(min(c_across(starts_with("LM")), na.rm = TRUE), 2),
    "Max cm" = round(max(c_across(starts_with("LM")), na.rm = TRUE), 2),
    # "N cm" = length(c_across(starts_with("LP")), na.rm = TRUE),
    "M n&pv com" = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2),
    "SD n&pv com" = round(sd(c_across(starts_with("LP")), na.rm = TRUE), 2),
    "Min n&pv com" = round(min(c_across(starts_with("LP")), na.rm = TRUE), 2),
    "Max n&pv com" = round(max(c_across(starts_with("LP")), na.rm = TRUE), 2)
  )

knitr::kable(df_quest_table,
             caption = "Mean, SD, Min, Max for classroom managament and ")





```


o	2 Skalen: 
	Classroom Management (5 Items + 3 selbstkonstruiert)
	Non- & paraverbal Communication (8 Items  abgeleitet aus Theorie (Kiel, Frey & Weiß)

